What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
stuff

\begin{itemize}
\item \underline{$min(e)=\c{V}$}: Expression that represent values are
  frequently passed to \eval. The majority of those, \packageValOneNodePercent,
  are inline constants (integers or doubles). The rest trivially evaluate to a
  value.\footnote{True as long as base functions such as \c{+} are not
  redefined. They typically aren't, but this is a limitation of this
  categorization.} In our corpus, \packageNbCallSitesUniqueActualValue call
  sites only ever see a simple values; the median number of times they are
  exercised is \packageMedianRunSitesUniqueActualValue, suggesting a possible
  lack of coverage. However, manual inspection reveals cases such as:
\begin{lstlisting}
 f1 <- eval(paste("A ~ ",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
  The code concatenates strings and \eval will simply return the string as is.
  From twenty randomly selected \evals, only \packageUsefulValueEvalPercent of
  them needed to use \eval.
%% The percentage of non default environment passed to \eval is
%% \packageMinimizedpercentenvirc when the minimized expression is a value. Some
%% sites which are passed a value, are also passed different minimized expressions.
%% For those ones, \packageNonDefaultEnvirValuePercent use a non-default
%% environment, and among the one that use a non-default environment,
%% \packageNonDefaultEnvirWithVarPercent have at least one minimized expression
%% with a variable inside.

\item \underline{$min(e)=\c{X}$}: Variables are the most common normal form.
  Variables subsume values, so they include arithmetic expressions in which a
  variable occurs. \packageNbSymbolVarSitePercent of variable expression are
  symbols, \ie just an \c{x}. A variable may refer to a promise and thus trigger
  computation the first time it is accessed.
  %% The
  %% \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of
  %% the call sites. The call sites without an explicit \c{envir} argument all use
  %% a specific \eval variant, \c{eval.parent}. Moreover, the \c{envir} argument is
  %% both explicit and different from \c{parent.frame()} in
  %% \packageMinimizedpercentenvirnonparenta\% of the sites, which suggests that
  %% when given a variable, \eval is often used to get value in a non-local,
  %% non-parent environment.
\item \underline{$min(e)=\c{\$}$}: A named lookup, written \c{x\$f}, can be used
  to look up a name in an environment or a column in a data frame. This category
  also groups indexing operators, \c{[]} and \c{[[]]}. The presence of these
  operators subsumes constants and variables.
%% It amounts for \packageNbSlotAccess sites, \ie
%% \packageSlotAccessPercent of the sites. The non-default, non-parent environment
%% percentage is here \packageMinimizedpercentenvirnonparentg.

>>>>

\begin{itemize}
\item \underline{$min(e)=\c{V}$}: Expression that represent values are
  frequently passed to \eval. The majority of those, \packageValOneNodePercent,
  are inline constants (integers or doubles). The rest trivially evaluate to a
  value.\footnote{True as long as base functions such as \c{+} are not
  redefined. They typically aren't, but this is a limitation of this
  categorization.} In our corpus, \packageNbCallSitesUniqueActualValue call
  sites only ever see a simple values; the median number of times they are
  exercised is \packageMedianRunSitesUniqueActualValue, suggesting a possible
  lack of coverage. However, manual inspection reveals cases such as:
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
  This concatenates to a string and \eval simply returns it as is.
  From twenty randomly selected \evals, only \packageUsefulValueEvalPercent of
  them needed to use \eval.
%% The percentage of non default environment passed to \eval is
%% \packageMinimizedpercentenvirc when the minimized expression is a value. Some
%% sites which are passed a value, are also passed different minimized expressions.
%% For those ones, \packageNonDefaultEnvirValuePercent use a non-default
%% environment, and among the one that use a non-default environment,
%% \packageNonDefaultEnvirWithVarPercent have at least one minimized expression
%% with a variable inside.

\item \underline{$min(e)=\c{X}$}: Variables are the most common normal form.
  Variables subsume values, so they include arithmetic expressions in which a
  variable occurs. \packageNbSymbolVarSitePercent of variable expression are
  symbols, \ie just an \c{x}. A variable may refer to a promise and thus trigger
  computation the first time it is accessed.
  %% The
  %% \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of
  %% the call sites. The call sites without an explicit \c{envir} argument all use
  %% a specific \eval variant, \c{eval.parent}. Moreover, the \c{envir} argument is
  %% both explicit and different from \c{parent.frame()} in
  %% \packageMinimizedpercentenvirnonparenta\% of the sites, which suggests that
  %% when given a variable, \eval is often used to get value in a non-local,
  %% non-parent environment.
\item \underline{$min(e)=\c{\$}$}: A name lookup, \c{x\$f}, is used
  can be used
  to look up a name in an environment or a column in a data frame. This category
  also groups indexing operators, \c{[]} and \c{[[]]}. The presence of these
  operators subsumes constants and variables.
%% It amounts for \packageNbSlotAccess sites, \ie
%% \packageSlotAccessPercent of the sites. The non-default, non-parent environment
%% percentage is here \packageMinimizedpercentenvirnonparentg.
